The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems

### 2012-04-30 shortRange.inhomo/alltext/pubilsh/main.tex
fix bug
small improves, argue the methods are not expensive

\documentclass[preprint]{revtex4}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\title{The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Pingwen Zhang}
% \email{pzhang@pku.edu.cn}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}

\begin{abstract}
  {
    In the present paper, we develop an accurate error estimate of the
    non-bonded short-range interactions for the inhomogeneous molecular
    systems.
    The root mean square force error is proved to be decomposed into
    three additive parts: the homogeneity error, the inhomogeneity error
    and the correlation error.
    % The homogeneity error is dominant
    % in the bulk regions.
    The magnitude of the inhomogeneity error, which
    is dominant in the interfacial regions, 
    can be more than one order of magnitude larger than the homogeneity
    error.
    % This is the reason why a direct simulation may waste
    % a huge amount of computational effort.
    This is the reason why a standard simulation with fixed
    cut-off radius is either less accurate if the cut-off is too small,
    or wastes considerable computational effort if the cut-off is too large.
    Therefore, based on the error estimate, the adaptive cut-off
    and long-range force correction methods are proposed to
    boost the efficiency and accuracy of the simulation, respectively.
    The
    effectiveness of the proposed methods are demonstrated by
    molecular dynamics 
    simulations of the liquid-vapor equilibrium and the nanoscale particle
    collision. Different roles of the homogeneity error and inhomogeneity
    error are also discussed.
  }
\end{abstract}

@@

\recheck{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the original interaction is kept, while outside it the
  interaction is screen by a shift function, so that goes to
  zero smoothly. The amount of Shifting is minor in most cases,
  however, it actually changes the way of
  modeling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  preferred and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical, wang2010optimizing}).
  % Shifting the direct part of the Ewald summation actually
  % violates the Coulomb's law in the way that depends on the
  % splitting parameter, so it should be treated carefully.
  % Here we would like to suggest treating the shifting approach
  % as a special case 
}
% In this paper, we focus on the systems in which
% atoms/particles are interacting via short-range interactions, because
% it is a good starting point of the study of more complex systems, for
% example, the systems with long-range electrostatic interactions.  The
% simulation results in the inhomogeneous systems are found to depend on
% a number of factors of treating the short-range interaction in the
% simulation. For example, the way of calculating the short-range
% interaction (simple cut-off method or Ewald
% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
%   lopez2006liquid, shi2006molecular, ismail2007application}, the
% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
%   shen2007comparative}, the way of long-range
% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
%   goujon2004monte} and the size and shape of the simulation
% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
% It should be noticed that the physical properties are the nature of
% the system, and should NOT depend on the details of the interaction
% calculation.

@@

In this work, we develop the error estimate of the short-range force
in inhomogeneous systems. We prove that the 
force error is comprised of a homogeneity error and an inhomogeneity
error, regardless of the particle-particle correlation outside the
cut-off radius.  In an inhomogeneous system composed by several bulk
regions connected by interfacial regions where the density changes
rapidly, an important observation is that the
inhomogeneity error plays a dominant role in the interfacial regions,
and can be more than one order of magnitude larger than
the error in the bulk regions. An
adaptive cut-off method is hereby proposed to equally distribute the
error across the simulation region, so that a considerable
computational effort can be saved in the bulk regions
while the precision of simulation is
preserved. We also proposed a long-range force correction (LFC) method
to screen out the contribution of the
inhomogeneity error, therefore,  the precision of
simulation is improved without much extra computational load.

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.
\recheck{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald summation~\cite{ewald1921die}, etc..
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cutting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demonstrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}
% Finally, conclusions are given in section
% \ref{sec:conclusion}.

@@

In this paper, for simplicity,
we will consider one-component systems, but
% we only consider the single-component system. Because
% this assumption simplifies the discussion, and
the error estimate for
the one-component system can be straightforwardly extended to the
multi-component systems.  We consider
the force error in the present paper, because the
applications are based on molecular dynamics simulations.
% Since the error estimate developed for the one-component system can be
% directly extended to multi-component system without substantial
% difficulty, the discussion in this paper will focus on one-component
% system for symplicity. 
Suppose the system is composed by $N$ identical particles located at
$\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
These particles are interacting via a short-range pairwise interaction
$u(\v r)$ with a cut-off radius $r_c > 0$. The corresponding force is
denoted by $\v f(\v r)$. 
% An infinite cut-off radius will lead to
% a precise calculation of interaction, but it is impractical.
% The error of computing interaction is mainly introduced by a finit
% value of the cut-off radius.
The force error mainly stems from the neglected interaction outside
the cut-off radius, so it is convenient to consider the complementary
of the cut-offed force that is defined by
\begin{align}
  \v f^c(\v r) =
  \left\{
  \begin{array}{ll}
    0, & \vert\v r\vert\leq r_c; \\
    \v f(\v r), & \vert\v r\vert > r_c.
  \end{array}
  \right.
\end{align}
We measure the force error at an arbitrary position in the system,
saying $\v r$, by adding a testing particle to that position.  We
assume all particles in the system exert forces on the testing
particle, whereas the testing particle does NOT exert any force on the
system.  The exact force and the computed force (or cut-offed force)
exerted by the system on the testing particle are denoted by ${\v
  F}(\v r)$ and $\tilde{\v F}(\v r)$, respectively.  The difference
between them, namely the \emph{error force}, is denoted by $\Delta\v
F(\v r) = \v F(\v r) - \tilde{\v F}(\v r)$, which can be expressed by
\begin{align}
  \Delta\v F(\v r) = \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n).
\end{align}
Where $\v n$ is the box vector, so the summation over $\v n$ indicates
that all periodic images of the system are considered. In a
homogeneous system, the surrounding of any particle is isotropic, so
the \emph{mean error force} vanishes: $\langle\Delta\v F(\v r)\rangle
= 0$. In contrast, the mean error force is not necessarily zero in an
inhomogeneous system:
\begin{align} \label{eqn:tmp3} %\nonumber
  \langle\Delta\v F(\v r)\rangle
  &=
  \big\langle
  \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n)
  \big\rangle 
  =
  \int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r',
\end{align}
where $\rho(\v r)$ denotes the particle number density at the position
$\v r$, and is periodically extended to $\mathbb R^3$. Notice that the
error force implicitly depends on the cut-off radius used for the
interaction calculation.

@@

@@

\subsection{Long-range Force correction}

@@

The idea of the long-range force correction is very similar to those
proposed by earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In those works, the density
profile is assumed to be inhomogeneous along one direction, and uniform
on the other two directions.
The
system is subdivided into slabs perpendicular to the inhomogeneous direction to
calculate the energy/force correction. The advantage of our force
correction is that it has \emph{no} uniformity restriction on the density
profile of the system, so can be used in a wider range of
inhomogeneous simulations.

@@

% The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
% method: in the bulk regions, the error is much smaller, therefore, it
% is a waste to use the same cut-off radius as the interfacial
% regions.
As mentioned before, the key idea of the adaptive cut-off simulation
is to use smaller cut-off
radius in the bulk regions, so that the RMS force error is uniformly
distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
present the adapted cut-off radius by a solid red line and all errors
by the same notations as in the Fig. \ref{fig:tmp2}. The control error
$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is almost the same as the maximum
error in the uniform cut-off simulation with $r_c^\ast=7.5$.
{
  In the rest of the paper, when we mention that ``the cut-off of
  the adaptive cut-off method is $r_c^\ast$'', we mean the
  control error is the maximum error of a uniform cut-off simulation
  using that cut-off $r_c^\ast$. In all the cases considered by
  the present paper, the maximum of
  the adapted cut-off radius is almost the same as $r_c^\ast$,
  and is sometimes marginally larger (no more than $r_c^\textrm{step}$).
}
The
cut-off distribution is calculated every 20,000 time steps, and is
refined twice by Eqn.~\eqref{eqn:rc-refine}. In the interfacial
regions, the same cut-off radius as the uniform cut-off simulation,
namely $7.5$, is used.  In the bulk
liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
which reduce the computational cost
by a factor of 4 and 10, respectively.
The error is uniformly distributed, except in the
liquid region where the real error is somewhat lower.
In contrast with the uniform
cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
vapor region is very sharp.
The similar phenomenon is observed in
Ref.~\cite{wang2011}.
The same as the uniform cut-off simulation, the
homogeneity error dominates in the bulk regions, while the
inhomogeneity error dominates in the interfacial region.

@@

In Fig. \ref{fig:tmp4}, the red solid line presents the $x$ component
of the 
correction force that is calculated every 40 time steps. The $y$ and
$z$ components are not shown because their magnitudes are negligible.
On the left interface, the correction force is along the positive
direction of $x$ axis, namely pointing right.  On the right interface,
the correction force is of the same magnitude but pointing
left. Therefore, the liquid density should be higher and the vapor
density should be lower than the corresponding uniform cut-off
simulation.  The real error (in green square) and the estimated
homogeneity error (in blue solid line) are all presented in
Fig. \ref{fig:tmp4}.  Clearly, the real error follows the homogeneity
error across the simulation region, which implies the contribution of
the inhomogeneity error is successfully removed, or is at least
negligible. In the bulk liquid region, the homogeneity error is
slightly overestimated, which is the same as the uniform and adaptive
cut-off simulations.

@@

\recheck{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate can be more general than the studied examples.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald summation, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}

>>>>

\documentclass[aps, pre, preprint]{revtex4}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

@@

\title{The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Pingwen Zhang}
% \email{pzhang@pku.edu.cn}
\affiliation{LMAM and School of Mathematical
  Sciences, Peking University}

\begin{abstract}
  {
    In the present paper, we develop an accurate error estimate of the
    non-bonded short-range interactions for the inhomogeneous molecular
    systems.
    The root mean square force error is proved to be decomposed into
    three additive parts: the homogeneity error, the inhomogeneity error
    and the correlation error.
    % The homogeneity error is dominant
    % in the bulk regions.
    The magnitude of the inhomogeneity error, which
    is dominant in the interfacial regions, 
    can be more than one order of magnitude larger than the homogeneity
    error.
    % This is the reason why a direct simulation may waste
    % a huge amount of computational effort.
    This is the reason why a standard simulation with fixed
    cut-off radius is either less accurate if the cut-off is too small,
    or wastes considerable computational effort if the cut-off is too large.
    Therefore, based on the error estimate, the adaptive cut-off
    and long-range force correction methods are proposed to
    boost the efficiency and accuracy of the simulation, respectively.
    The way of correcting the long-range contribution of pressure
    is also developed for the inhomogeneous system.
    The
    effectiveness of the proposed methods are demonstrated by
    molecular dynamics 
    simulations of the liquid-vapor equilibrium and the nanoscale particle
    collision. Different roles of the homogeneity error and inhomogeneity
    error are also discussed.
  }
\end{abstract}

@@

{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the original interaction is kept, while outside it the
  interaction is screened by a shift function, so that it goes to
  zero smoothly and rapidly. The amount of shifting is minor in most cases,
  however, it actually changes the way of
  modeling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  preferred and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical}).
  % Shifting the direct part of the Ewald summation actually
  % violates the Coulomb's law in the way that depends on the
  % splitting parameter, so it should be treated carefully.
  % Here we would like to suggest treating the shifting approach
  % as a special case 
}
% In this paper, we focus on the systems in which
% atoms/particles are interacting via short-range interactions, because
% it is a good starting point of the study of more complex systems, for
% example, the systems with long-range electrostatic interactions.  The
% simulation results in the inhomogeneous systems are found to depend on
% a number of factors of treating the short-range interaction in the
% simulation. For example, the way of calculating the short-range
% interaction (simple cut-off method or Ewald
% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
%   lopez2006liquid, shi2006molecular, ismail2007application}, the
% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
%   shen2007comparative}, the way of long-range
% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
%   goujon2004monte} and the size and shape of the simulation
% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
% It should be noticed that the physical properties are the nature of
% the system, and should NOT depend on the details of the interaction
% calculation.

@@

In this work, we develop the error estimate of the short-range interaction,
and the long-range force and pressure corrections
for the inhomogeneous systems. We prove that the 
force error is comprised of a homogeneity error and an inhomogeneity
error, regardless of the particle-particle correlation outside the
cut-off radius.  In an inhomogeneous system composed by several bulk
regions connected by interfacial regions where the density changes
rapidly, an important observation is that the
inhomogeneity error plays a dominant role in the interfacial regions,
and can be more than one order of magnitude larger than
the error in the bulk regions. An
adaptive cut-off method is hereby proposed to equally distribute the
error across the simulation region, so that a considerable
computational effort can be saved in the bulk regions
while the precision of simulation is
preserved. We also proposed a long-range force correction (LFC) method
to screen out the contribution of the
inhomogeneity error, therefore,  the precision of
simulation is improved without much extra computational load.

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald family algorithms~\cite{ewald1921die, darden1993pme, essmann1995spm, deserno1998mue1}, etc..
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cutting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demonstrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}
% Finally, conclusions are given in section
% \ref{sec:conclusion}.

@@

In this paper, for simplicity,
we will consider one-component systems, but
% we only consider the single-component system. Because
% this assumption simplifies the discussion, and
the error estimate for
the one-component system can be straightforwardly extended to the
multi-component systems.  We consider
the force error in the present paper, because the
applications are based on molecular dynamics simulations.
% Since the error estimate developed for the one-component system can be
% directly extended to multi-component system without substantial
% difficulty, the discussion in this paper will focus on one-component
% system for symplicity. 
Suppose the system is composed by $N$ identical particles located at
$\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
These particles are interacting via a short-range pairwise interaction
$u(\v r)$ with a cut-off radius $r_c > 0$.
The corresponding force is
denoted by $\v f(\v r)$. 
Most short-range interactions satisfy $\vert
u(r)\vert\leq C r^{-m}$, $m>3$, which guarantees an absolute convergence of the
energy.
Throughout the paper, the only assumptions made on the interaction are:
(1) the interaction is short-ranged and (2)
it is calculated by the cut-off method.
Therefore, our approach works for a large group of widely used interactions, 
for example, the Lennard-Jones interaction, the Buckingham interaction,
the direct part of Ewald family algorithms, and so forth.
% An infinite cut-off radius will lead to
% a precise calculation of interaction, but it is impractical.
% The error of computing interaction is mainly introduced by a finit
% value of the cut-off radius.

The force error stems from the neglected interaction outside
the cut-off radius, so it is convenient to consider the complementary
of the cut-offed force that is defined by
\begin{align}
  \v f^c(\v r) =
  \left\{
  \begin{array}{ll}
    0, & \vert\v r\vert\leq r_c; \\
    \v f(\v r), & \vert\v r\vert > r_c.
  \end{array}
  \right.
\end{align}
We measure the force error at an arbitrary position in the system,
saying $\v r$, by adding a testing particle to that position.  We
assume all particles in the system exert forces on the testing
particle, whereas the testing particle does NOT exert any force on the
system.  The exact force and the computed force (or cut-offed force)
exerted by the system on the testing particle are denoted by ${\v
  F}(\v r)$ and $\tilde{\v F}(\v r)$, respectively.  The difference
between them, namely the \emph{error force}, is denoted by $\Delta\v
F(\v r) = \v F(\v r) - \tilde{\v F}(\v r)$, which can be expressed by
\begin{align}
  \Delta\v F(\v r) = \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n).
\end{align}
Where $\v n$ is the box vector, so the summation over $\v n$ indicates
that all periodic images of the system are considered. In a
homogeneous system, the surrounding of any particle is isotropic, so
the \emph{mean error force} vanishes: $\langle\Delta\v F(\v r)\rangle
= 0$. In contrast, the mean error force is not necessarily zero in an
inhomogeneous system:
\begin{align} \label{eqn:tmp3} %\nonumber
  \langle\Delta\v F(\v r)\rangle
  &=
  \big\langle
  \sum_{\v n}\sum_{j}\, \v f^c(\v r - \v r_j + \v n)
  \big\rangle 
  =
  \int_{\mathbb R^3}\v f^c(\v r - \v r')\rho(\v r')\,\d d\v r',
\end{align}
where $\rho(\v r)$ denotes the particle number density at the position
$\v r$, and is periodically extended to $\mathbb R^3$. Notice that the
error force implicitly depends on the cut-off radius used for the
interaction calculation.

@@

Since the density profile of the system changes
very slow comparing with the typical time step used in the MD simulation,
the cut-off distribution is not calculated every time step.
Instead,
for example, in the liquid-vapor equilibrium simulation
(see Sec.~\ref{sec:tmp2.1}),
the cut-off distribution is calculated every 20,000 time steps,
so the extra load of adapting the cut-off is only marginal
in the simulation, i.e. proportional to $ \frac{M}{20,000}N\log N$.

@@

\subsection{Long-range force correction}

@@

In most cases, the ensemble average of the error force
does not change very fast comparing with the typical time step used in a MD
simulation. Therefore, it is not necessary to calculate
the correction force every time step. Instead, for example,
we calculate it every 40 time steps in the liquid-vapor equilibrium
testing system (see Sec.~\ref{sec:tmp2.1}), which takes
no more than 10\% of the total computational cost.
If the long-range interaction calculations (which needs FFTs anyway)
are involved, this ratio should be even lower.
The idea of the long-range force correction is very similar to those
proposed by earlier works~\cite{guo1997long, mecke1997molecular,
  janecek2006long, shen2007comparative}. In those works, the density
profile is assumed to be inhomogeneous along one direction, and uniform
on the other two directions.
The
system is subdivided into slabs perpendicular to the inhomogeneous direction to
calculate the energy/force correction. The advantage of our force
correction is that it has \emph{no} uniformity restriction on the density
profile of the system, so can be used in a wider range of
inhomogeneous simulations.

@@

% The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
% method: in the bulk regions, the error is much smaller, therefore, it
% is a waste to use the same cut-off radius as the interfacial
% regions.
As mentioned before, the key idea of the adaptive cut-off simulation
is to use smaller cut-off
radius in the bulk regions, so that the RMS force error is uniformly
distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
present the adapted cut-off radius by a solid red line and all errors
by the same notations as in the Fig. \ref{fig:tmp2}. The control error
$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is almost the same as the maximum
error in the uniform cut-off simulation with $r_c^\ast=7.5$.
{
  In the rest of the paper, when we mention that ``the cut-off of
  the adaptive cut-off method is $r_c^\ast$'', we mean the
  control error is the maximum error of a uniform cut-off simulation
  using that cut-off $r_c^\ast$. In all the cases considered by
  the present paper, the maximum of
  the adapted cut-off radius is almost the same as $r_c^\ast$,
  and is sometimes marginally larger (no more than $r_c^\textrm{step}$).
}
The
cut-off distribution is calculated every 20,000 time steps, and is
refined twice by Eqn.~\eqref{eqn:rc-refine}.
Due to this low cut-off redistribution frequency,
the extra cost of this adaptive method is only marginal
comparing with the total computational cost.
In the interfacial
regions, the same cut-off radius as the uniform cut-off simulation,
namely $7.5$, is used.  In the bulk
liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
which reduce the computational cost
by a factor of 4 and 10, respectively.
The error is uniformly distributed, except in the
liquid region where the real error is somewhat lower.
In contrast with the uniform
cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
vapor region is very sharp.
The similar phenomenon is observed in
Ref.~\cite{wang2011}.
The same as the uniform cut-off simulation, the
homogeneity error dominates in the bulk regions, while the
inhomogeneity error dominates in the interfacial region.

@@

In Fig. \ref{fig:tmp4}, the red solid line presents the $x$ component
of the 
correction force that is calculated every 40 time steps.
The extra computational cost is no more than 10\% of the total
computational costs in all the tested cases.
The $y$ and
$z$ components are not shown because their magnitudes are negligible.
On the left interface, the correction force is along the positive
direction of $x$ axis, namely pointing right.  On the right interface,
the correction force is of the same magnitude but pointing
left. Therefore, the liquid density should be higher and the vapor
density should be lower than the corresponding uniform cut-off
simulation.  The real error (in green square) and the estimated
homogeneity error (in blue solid line) are all presented in
Fig. \ref{fig:tmp4}.  Clearly, the real error follows the homogeneity
error across the simulation region, which implies the contribution of
the inhomogeneity error is successfully removed, or is at least
negligible. In the bulk liquid region, the homogeneity error is
slightly overestimated, which is the same as the uniform and adaptive
cut-off simulations.

@@

{
  We want to stress again the main research interest of the present paper is the
  error estimate, the proposed adaptive cut-off and long-range
  correction methods. The examples are used to demonstrate
  the validity of these theoretical results. The applications
  of the error estimate can be more general than the studied examples.
  Other kind the short-range interaction (not only the Lennard-Jones
  but also the Buckingham,
  the direct part of the Ewald family algorithms, etc.),
  and other kinds of inhomogeneity
  (not only  planar and merging spherical interfaces)
  can be easily studied by the error estimates and the proposed methods.
  The error study of
  more realistic systems requires the error estimates of the long-range
  algorithms, and careful comparisons with the short-range error.
  Since the present paper is focusing on the short-range
  interactions, and the space is limited,
  they will be given in the future work.
}
